Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/propane.tex
small changes to sec 4

\sysname allows the operator to configure the network with the
abstraction that he or she has centralized control over routing.
Specifically, the operator simply provides a set of high-level constraints
that describe the 
different routes traffic may (or may not) take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network from the previous section, we first express the idea that for routes leading to our customer,
we prefer using \CD{R1} over \CD{R2} (Policy P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define ExitCust = \Exit(R1 \Prefer R2)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}.

@@

Since routing allows transit traffic (\EG, traffic entering from
\CD{Peer} and leaving through \CD{Prov}), we define a new policy to implement this restriction separately, using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints. 
%union (\Union), intersection (\Intersect), and negation (\NOT) to
%specify the appropriate sets of paths.
%
%% \begin{lstlisting}[mathescape=true]
%% define PP = Peer or Prov
%% define PPTransit = $enter(PP) \AND exit(PP)$
%% define CustTransit = $later(Cust) \AND later(Prov)$

%% define NoTransit = {
%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
%% }
%% \end{lstlisting}
\begin{code}
\Define PP = Peer \OR Prov
\Define PPTrans   = \Enter(PP) \AND \Exit(PP)
\Define CustTrans = \Later(Cust) \AND \Later(Prov)
\Define NoTrans   = \{\True \Path \NOT{}PPTrans \AND \NOT{}CustTrans\}
\end{code}
\noindent
The \CD{NoTrans} constraint above ensures that requirements P2 and P5 are satisfied. It says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}. Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failure cases.

@@

As in the backbone example, we can combine these constraints
logically to specify the network-wide policy.
However, in addition to constraints on the shape of paths,
\sysname allows the operator to specify constraints on the BGP control plane.
For instance, a constraint on aggregation is included to ensure that
aggregation for global prefixes is performed from
locations inside (\In) the network to locations outside (\Out). 
In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} 
(which we assume is defined earlier using an appropriate prefix such 
as \CD{74.3.28.0/24})
when advertised outside the datacenter.

@@

As before, once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. \sysname also checks for safety against aggregation-induced black holes.
%It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.

>>>>

\sysname allows the operator to configure the network with the
abstraction that he or she has centralized control over routing.
Specifically, the operator simply provides a set of high-level constraints
that describe the 
different routes traffic may (or may not) take and their relative preferences.
\sysname specifications are written modularly via a series
of declarations.
%These definitions allow users to express the three
%major elements of any \sysname specification:  \emph{prefixes},
%\emph{paths} and \emph{policies}.
For example, to begin specification of the backbone
network from the previous section, we first express the idea that for routes leading to our customer,
we prefer using \CD{R1} over \CD{R2} (policy P3 from Figure~\ref{fig:example1}):
%\begin{lstlisting}[mathescape=true]
%define ExitCust = $exit(R_1 \gg R_2)$
%\end{lstlisting}
\begin{code}
\Define ExitCust = \Exit(R1 \Prefer R2)
\end{code}
This  statement defines a set of \emph{ranked paths}, which includes
all paths (and only those paths) for which traffic exits our network
through either router \CD{R1} or \CD{R2}.  The paths that exit through \CD{R1}
are preferred (\Prefer) to those that exit through \CD{R2}.  As we
describe in the next section, the \Exit\ predicate, as well as other
path predicates used later in this section, is simply a shorthand for 
a particular regular expression over paths that is expressible in our policy
language.

@@

Since by default routing allows transit traffic (\EG, traffic entering from
\CD{Peer} and leaving through \CD{Prov}), we separately define a
policy to enforce P2 and P5 from Figure~\ref{fig:example1}, using conjunction (\AND),
disjunction (\OR) and negation (\NOT) of constraints. 
%union (\Union), intersection (\Intersect), and negation (\NOT) to
%specify the appropriate sets of paths.
%
%% \begin{lstlisting}[mathescape=true]
%% define PP = Peer or Prov
%% define PPTransit = $enter(PP) \AND exit(PP)$
%% define CustTransit = $later(Cust) \AND later(Prov)$

%% define NoTransit = {
%%     $\path{true}{\neg PPTransit \AND \NOT CustTransit}$
%% }
%% \end{lstlisting}
\begin{code}
\Define PP = Peer \OR Prov
\Define PPTrans   = \Enter(PP) \AND \Exit(PP)
\Define CustTrans = \Later(Cust) \AND \Later(Prov)
\Define NoTrans   = \{\True \Path \NOT{}PPTrans \AND \NOT{}CustTrans\}
\end{code}
\noindent
The \CD{NoTrans} constraint above says that for any prefix, traffic should never both enter and exit the network from \CD{Peer} or \CD{Prov}. Similarly it prevents traffic from ever following paths that leave our network and later passing through both \CD{Prov} and \CD{Cust}.  To implement both \CD{Routing}
and \CD{NoTrans} simultaneously, we simply conjoin them: \CD{Routing \AND{} NoTrans}.
%
%% \begin{lstlisting}[mathescape=true]
%% Routing $\AND$  NoTransit
%% \end{lstlisting}
%
These constraints capture the entire policy. From them, \sysname will generate per-device import and export filters, local preferences,
MED attributes, and community tags to ensure that the policy is
implemented correctly under all failure cases.

@@

As in the backbone example, we can logically conjoin these constraints
to specify the network-wide policy.
However, in addition to constraints on the shape of paths,
\sysname allows the operator to specify constraints on the BGP control plane.
For instance, a constraint on aggregation is included to ensure that
aggregation for global prefixes is performed from
locations inside (\In) the network to locations outside (\Out). 
In this case, \CD{PG1} and \CD{PG2} will use the aggregate \CD{PG} 
(which we assume is defined earlier using an appropriate prefix such 
as \CD{74.3.28.0/24})
when advertised outside the datacenter.

@@

As before, once \sysname compiles the policy, it is guaranteed to hold under all possible failure scenarios. \sysname also ensures safety against aggregation-induced black holes.
%It can efficiently determine a lower bound on the number of failures necessary to black hole traffic given the user's policy, topology, and placement of specific aggregates.
